---
title: "HW1"
author: "Matthew Ma"
date: "2022-09-24"
output: github_document
---

```{r, eval=FALSE}
library(tidyverse)
```


```{r}
data("penguins", package = "palmerpenguins")
```

## `r The penguins data set contains equal number of categorical variables as the numerical variables. As I noticed, the year range is about 2 years from 2007 to 2009. The penguins are sourced from three islands named: "Torgersen", "Biscoe" and "Dream" varied by 3 species: "Adelie", "Gentoo", and "Chinstrap". Each penguin's bill length and depth are measured, their body mass and flipper length are also recorded. This data set has got 344 rows and 8 columns. The mean flipper length is 200.9mm which is very close to its median 197, so it should look nearly symmetric. `

```{r}
nrow(penguins)
ncol(penguins)
summary(penguins)
```

```{r}
ggplot() + 
  geom_point(data = penguins, mapping = aes( x = bill_length_mm, y = 
  flipper_length_mm, color = species))
ggsave("scatterplot.pdf")
```

```{r}

df = tibble(
  rs = rnorm(10),
  vec_logic = rs > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_fac = c( "low", "medium", "high", "low", "medium", "high", "low", "medium", "high", "low")
)

pull(df, var = rs)
pull(df, var = vec_logic)
pull(df, var = vec_char)
pull(df, var = vec_fac)

mean(df$rs)
mean(df$vec_logic)
mean(df$vec_char)
mean(df$vec_fac)
summary(df)

```

## `r While trying to take the means of the variables, the numeric variable random sample works, the character and factor variables do not. To my surprise, the logic factor also works.`

```{r, eval = }

```

